Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 robdml.tex
tex

@@

\subsection{Effectiveness of HM}

>>>>

Recall that triplet-based model is already prone to collapse with very hard
examples, even if they are unperturbed.
%
Similarly, the model is expected to collapse with excessively hard adversarial
examples as well.
%
As shown in the last three columns of \cref{tab:desth}, almost all combinations
will result in model collapse as long as the destination hardness is softhard,
distance, or hardest.
%
The only exception is the combination of distance and hardest.
%
We speculate the  \oo{TODO}
The $E[H]$ of distance and hardest sampling are empirically observed very close.
%

And the model can be easier to collapse with adversarially perturbed hard
examples

@@

The proposed hardness manipulation is effective.

\subsection{Efficiency of Hardness Manipulation}
